Online Appendix for \\ Enemy at the Gates: Variation in Economic Growth from Civil Conflict

### 2016-01-23 LaTeX/TeX/Manuscript/Abstract.tex
reorg for final submission to jcr

% Version submitted to MPSA:
Within the conflict literature there has been much disagreement about the relationship between civil wars and state economic performance. While civil war is often associated with poor economic performance, some states have managed to weather domestic armed conflict during periods of robust growth. We find that this disagreement results from not accounting for the spatial distribution of conflict within a country. Literature in economics has recently stressed the importance of major cities to development and economic growth. We hypothesize that the economic impact of civil conflict is contingent on the conflict's location relative to major urban centers within a state. We use subnational data on the location of conflict relative to urban areas to test the impact of domestic conflict on annual GDP growth. In doing so, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries. By doing so, we are able to resolve tensions in the literature regarding the relationship between economic performance and civil wars. We find that the proximity of civil war to major urban centers is negatively correlated with economic growth and use simulations to show that the estimated marginal effect of civil war proximity can mean the difference between robust growth and stagnation.

>>>>

% Version submitted to MPSA:
There has been much disagreement about the relationship between civil wars and state economic performance. While civil war is often associated with poor economic performance, some states have managed robust growth despite periods of domestic armed conflict. We find this disagreement results from not accounting for the spatial distribution of conflict within a country. A robust literature in economics stresses the role major cities play in economic growth. We hypothesize that the economic impact of civil conflict is contingent on the conflict's location relative to major urban centers within a state. We use subnational data on the location of conflict relative to urban areas to test the impact of domestic conflict on annual GDP growth. In doing so, we bridge the economic development literature on the importance of cities with extant literature on the effect of armed conflict to provide a novel explanation for the paradox of high macroeconomic growth in conflict ridden countries.
